\plaintitle

### 2015-11-07 Paper/paper.tex
Added command that removes copyright section
Added draft for RRL

@@

>>>>

% remove copyright
\makeatletter
\def\@copyrightspace{\relax}
\makeatother

@@

\section{Related Work}

There is a limited number of papers that specifically discuss SystemOne. These papers
mostly focus on the various modules that provide different kinds of functionality for SystemOne
and the features to be created rather than the speed and feasibility of the use of the system.
Suayan (1997) developed one of the first registration systems used in UPLB called the
UPLB RegisNet. This system was designed to automate the pre-enlistment of subjects for
students.

Meanwhile, the UPLB Academic Information System was created and had support for
modularity. Through its modularity, various modules were created for it. Cruz (2001) created a
Subjects module that gave it the ability to add, edit, and delete subjects from a list of subjects and
Almodiel (2001) developed a module that allowed teachers to add, search, and view the grades of
a student in their respective classes. Enrique (2001) then developed a Schedule of Classes
module that was responsible for managing and viewing the schedule of a subject, a room, or a
teacher.

The UPLB University Data Resource Network is another system used in UPLB. It was
created in 2003 and was also designed to be able to support modules. Gimotea (2003) was the
one who developed the Curricular, Degree Course, Class Schedules, and Room Assignment
Module which gave it functionalities similar to those that registration systems have like the
manipulation of schedules and rooms for classes and courses.
After a few years, Javier, et al. (2005) developed the first version of UPLB’s Online
Registration System called SystemOne. This system was also extensible through modularity. In
this version, SystemOne used the Java programming language for implementing the Enlistor and
Registrar module, PHP 5 for the Department module and MySQL as the Database Management
System (DBMS).

Because SystemOne was designed to be extensible through its support for modules, various
modules for it has been developed around the same time as the development of original
SystemOne. Curativo, et al. (2005) developed a web service module so that SystemOne can be
accessible using a web browser. Before that, users had to use the Java application for SystemOne
for them to be able to access it. Cardenas, et al. (2005) also developed another module called the
Data Manager Interface (DMI) which was responsible for allowing SystemOne to access a
Database Management System (DBMS) and converting data given by the Office of the
University Registrar through the REGIST system into a database that can be understood by
SystemOne. Both of these modules also used the Java programming language and supported the
MySQL DBMS.

In the year 2010, the development of the UPLB SystemOne V2 began. This version also
used the Java programming language and the MySQL DBMS and was also modular. However,
the difference of this new system from the previous system was that even the core functions were
divided into modules and was developed separately.

Payoyo (2010) developed the Announcement, Registrar and Observer Module for
SystemOne V2 which allowed support for announcement and gave representatives from the
registrar an interface to manage the courses to be offered among other things. Granada (2010)
developed the Subject Planner and Student’s Checklist which gave students the ability to view
their checklist and plan their schedule of subjects.

At the same time, Guevarra (2010) developed a Mobile Bluetooth Interface for Nokia 60
Series Smartphones using Symbian C++. This allowed users of the Nokia 60 Series Smartphones
to access SystemOne on their smartphones.

In 2012, the third and current version of SystemOne was developed by the SystemOne
Development Team. This system, unlike the previous versions that used Java, used the PHP
programming language along with the MySQL DBMS. Like the second version, this system
supports modules and its core functions are also implemented as modules.

Unfortunately, it is now a known fact that Java is rather slow compared to the alternatives.
Jelovic (n.d.) stated in one of his online articles that “anybody that has ever used a non-trivial
Java program or has programmed in Java knows that Java is slower than native programs written
in C++”. This is just one among the number of criticisms that Java receives when it comes to its
speed. Despite this, Java is known to be easy to use and was designed to be good for
network-based applications.

Another programming language used in the implementations of SystemOne is the PHP
programming language. This programming language is also known to be slow when it comes to
large-scale web applications. What more is that the flavor of PHP that was used in the third
version called Suhosin is known to be a bit slower than than the original PHP.

There was one study that focused on the speed and response time of SystemOne. Crespo
(2014) wrote a study entitled “Comparing the Response and Rendering Time of PHP-based
against Javascript-based SystemOne”. This study did a comparison on how much faster or slower
SystemOne would be had it been implemented in Javascript using the NodeJS interpreter. Her
study detailed the performance of her own Javascript-based implementation against the
PHP-based implementation. The results of her study showed that the Javascript-based
implementation yielded a 52 percent increase in overall speed.

These results seem to be very promising considering the fact that NodeJS is known to not be
able to take full advantage of a server computer that has multiple cores yet. This shows that
SystemOne could have been faster if the right choices were made.
These studies show a history of Online Registration Systems used in UPLB. It can be seen in
the papers and articles cited that the use of the best and fastest technology has not really been
given consideration.

\section{Methodology}

\subsection{Database}

The system will utilized three database systems. These database systems are as
follows:
\begin{enumerate}
\item High-Speed Read and Write Storage System - This will be shared across all
clusters. This needs to high speed because it will used to store information
that change very fast and is read repeatedly such as the number of slots for
every subject.

\item High-Speed Read and Medium-Speed Write Relational Database System - Also 
shared across all clusters, this will contain data and information that are not
changed often but are read a repeatedly a lot such as the information for subjects
and their dependencies, user accounts, and recommended courses.

\item Persistent Relational Database System - This will be used as the permanent
storage for all data. The other two storage and database systems will synchronize
to this database at specific intervals.
\end{enumerate}

\subsection{Backend}

The backend will be a server that serves a Representational State Transfer (REST)
Application Programming Interface (API) through the Hypertext Transfer Protocol
(HTTP). The system's backend shall have multithreading support. A thread will be 
spawned for every successful HTTP connection. This thread will handle its own
associated connection and wait for a command before processing it and giving a 
reply. If a command is not received or completed after a specified amount of
time, a timeout will occur and the connection will be dropped along with its
corresponding thread being deallocated from the memory.

\subsubsection{Conflict Checking}

Every time a modification or addition is done on a student's schedule, the 
backend will check for conflicts before executing the specified action. 
To do this, a bitwise AND will be done on the current user's schedule and the
schedule of the subject to be inserted. If the resulting value is not 0 then
an error reply will be sent.

\subsection{Frontend}
